Bayesian Exploration in Deep Reinforcement Learning

### 2022-01-28 papers/main.tex
TEMPORARY DEPLOY COMMIT

\subsection{Details and Hyperparameters}
We compare our method with NoisyNet~\citep{fortunato_noisy_2019} on four different
environments in the OpenAI Gym~\citep{brockman_openai_2016-2}. The hyperparameters
are the same as those described in \cite{han_nrowan-dqn_2020}. Our method additionally
has hyperparameters related to the functional KL-divergence. These are shown in
Table~\ref{tab:hyperparams}.

@@

\subsection{Uninformative Prior}
First, it is interesting to see how our method will compare to NoisyNet
in environments without the advantage of prior knowledge. The training curves
of our model compared to that of standard NoisyNet-DQN on the four selected OpenAI
Gym~\citep{brockman_openai_2016} enivornments is shown in Figure~\ref{fig:training_curves}.
We hypothesize that the added KL-term will push the algorithm keep weight uncertinaty high
in order to keep a higher uncertainty in the output. While both methods are able to
find an optimal policy in Cartpole, our method uses considerably fewer frames
to do so.

@@

\cite{fortunato_noisy_2019} noted that the learned variance in their weight increased
in some games despite there existing an optimal deterministic solution, and the loss
gives no incentive to maintain any uncertainty. Figure~\ref{fig:mean_std} shows
the mean-absolute standard deviation for the penultimate and final layer. It is 
interesting to see that the standard deviation for NoisyNet continous to decrease
throughout the training, while LFM decreases faster, but then flattens out earlier.
This seems to indicate that it has found a stable policy, where optimizing further would
be overfitting to noise.

>>>>

\subsection{Details and Hyperparameters}
We compare our method with NoisyNet~\citep{fortunato_noisy_2019} on four different
environments in the OpenAI Gym~\citep{brockman_openai_2016-2}. The hyperparameters
are the same as those described in \cite{han_nrowan-dqn_2020}. Our method additionally
has hyperparameters related to the functional KL-divergence. These are reported in
Table~\ref{tab:hyperparams}.

@@

\subsection{Uninformative Prior}
First, it is interesting to see how our method will compare to NoisyNet
in environments without the advantage of prior knowledge. The training curves
of our model compared to that of standard NoisyNet-DQN on the four selected OpenAI
Gym~\citep{brockman_openai_2016} environments is shown in Figure~\ref{fig:training_curves}.
We hypothesize that the added KL-term will push the algorithm to retain weight uncertainty high
in order to keep a higher uncertainty in the output. While both methods can
find an optimal policy in Cartpole, our method uses considerably fewer frames
to do so.

@@

\cite{fortunato_noisy_2019} noted that the learned variance in their weight increased
in some games despite there existing an optimal deterministic solution, and the loss
provides no incentive to maintain any uncertainty. Figure~\ref{fig:mean_std} shows
the mean-absolute standard deviation for the penultimate and final layer. It is 
interesting to see that the standard deviation for NoisyNet continues to decrease
throughout the training while LFM decreases faster, but then flattens out earlier.
This seems to indicate that it has found a stable policy, where optimizing further would
be overfitting to noise.
